\LARGE \bf On the use of vehicle categorization and context information for messages forwarding in VANETs

### 2016-09-16 paperITSC.tex
related work commit text

We consider a scenario where vehicles create messages to be forwarded for a globally known fixed infrastructure. However, to deliver these messages, intelligent forwarding decisions are required. In this regard, our protocol uses three different schemes, i.e., vehicle distance to the destination, vehicle speed and its category. Additionally, we used a mechanism called \emph{RateTimeToSend} which uses traffic flow information to control message forwarding rate. To evaluate the performance of our protocol, we performed extensive set of simulations by considering different parameters.

@@

In \cite{magf2009}, the authors addressed the problem of rapid topology changes and frequent disconnections in VANETs. They assumed that the vehicle is aware of its own movement and its neighbors, and uses this information to select the best next hop to carry the message. They concluded that using a combination of position, speed and direction has a significant performance improvement in terms of data delivery ratio and latency.

A geocast forwarding protocol for VANETs was proposed in \cite{vcarp2012}. The protocol uses context information in order to make more accurate decision in the forwarding process. Besides, it used a shared cache mechanism to prevent packet losses, due to full caches. Using shared cache mechanism along with position, distance to destination and direction, they achieved an improvement of 40\%, in terms of packet delivery ratio. Additionally, they reduced the overhead to 89\%, as compared with \cite{maihofer2004}.

In \cite{move2005} five opportunistic forwarding schemes were presented and compared in terms of overhead, success rate and latency. In the first scheme, the vehicle gets the message and carries it towards the destination, without exchanging data with other nodes. Whereas in the second scheme, the message is broadcasted to all nodes, moving towards the destination. In the remaining schemes they used the context related information, i.e., distance, speed, and heading.

In order to better utilize node mobility and deal with connectivity issues, \emph{GeoMob} \cite{zhang2014} was proposed. The scheme exploits the different mobility patterns of the two category of vehicles, taxicabs and buses. Furthermore, a global traffic distribution was used to create cluster regions and forward the message through them. However, they used dynamic clusters which generates overhead. Moreover, their solution requires the global traffic distribution which may not be available. These requirements could degrades performance or even make the solution impracticable.

A lightweight vehicular ontology was proposed in CAOVA \cite{caova2012}, with the aim to share and reuse information about accidents. Based on the ontology, they generate warnings to improve the safety on the roads. Similarly \cite{groza2014} proposed a vehicular network ontology to facilitate the interoperability at application level. They showed the capabilities of ontologies to enhance the information collection, representation and its use for preventing accidents.

>>>>

We consider a scenario where vehicles create messages to be forwarded for a globally known fixed infrastructure. However, to deliver these messages, intelligent forwarding decisions are required. In this regard, our protocol uses three different schemes, i.e., vehicle distance to the destination, vehicle speed, and its category. Additionally, we used a mechanism called \emph{RateTimeToSend} which uses traffic flow information to control message forwarding rate. To evaluate the performance of our protocol, we performed an extensive set of simulations by considering different parameters.

@@

In \cite{magf2009}, the authors addressed the problem of rapid topology changes and frequent disconnections in VANETs. They assumed that the vehicle is aware of its own movement and its neighbors, and uses this information to select the best next hop to carry the message. They concluded that using a combination of position, speed and direction have a significant performance improvement in terms of data delivery ratio and latency.

A geocast forwarding protocol for VANETs was proposed in \cite{vcarp2012}. The protocol uses context information in order to make a more accurate decision in the forwarding process. Besides, it used a shared cache mechanism to prevent packet losses, due to full caches. Using shared cache mechanism along with position, distance to destination and direction, they achieved an improvement of 40\%, in terms of packet delivery ratio. Additionally, they reduced the overhead to 89\%, as compared with \cite{maihofer2004}.

In \cite{move2005} five opportunistic forwarding schemes were presented and compared in terms of overhead, success rate, and latency. In the first scheme, the vehicle gets the message and carries it towards the destination, without exchanging data with other nodes. Whereas in the second scheme, the message is broadcasted to all nodes, moving towards the destination. In the remaining schemes, they used the context related information, i.e., distance, speed, and heading.

In order to better utilize node mobility and deal with connectivity issues, \emph{GeoMob} \cite{zhang2014} was proposed. The scheme exploits the different mobility patterns of the two categories of vehicles, taxicabs and buses. Furthermore, a global traffic distribution was used to create cluster regions and forward the message through them. However, they used dynamic clusters which generate overhead. Moreover, their solution requires the global traffic distribution which may not be available. These requirements could degrade performance or even make the solution impracticable.

A lightweight vehicular ontology was proposed in CAOVA \cite{caova2012}, with the aim to share and reuse information about accidents. Based on the ontology, they generate warnings to improve the safety on the roads. Similarly, \cite{groza2014} proposed a vehicular network ontology to facilitate the interoperability at the application level. They showed the capabilities of ontologies to enhance the information collection, representation and its use for preventing accidents.
